---
title: "Reproducibility Report: System and R Environment Summary"
author: "Ivan Hanigan"
date: "2024-10-10"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("R/load_packages.R")
load_packages(force_install=F)
```

This report summarises our R environment, OS, CPU, and memory for reproducibility. This report will capture the key details for anyone wishing to replicate our computational setup.

## System Information

### Operating System (OS) Info

This section retrieves the operating system and system kernel details.

```{r os-info}
Sys.info()
```

### CPU and Memory Information (Linux/macOS)

Below is the CPU and memory information retrieved from system commands.

```{r system-info}
# CPU Info
system("lscpu", intern = TRUE)

# Memory Info
system("free -h", intern = TRUE)
```

## Note about code editor

Note that the Rstudio editor version gave errors and so the Emacs ESS editor was used instead.

The Rstudio Editor version that failed was 

```
RStudio 2023.06.1+524 "Mountain Hydrangea" Release (547dcf861cac0253a8abb52c135e44e02ba407a1, 2023-07-05) for Ubuntu Focal
Mozilla/5.0 (X11; Linux x86_64) AppleWebKit/537.36 (KHTML, like Gecko) rstudio/2023.06.1+524 Chrome/110.0.5481.208 Electron/23.3.0 Safari/537.36
```


## R Environment

The session information for R 
```{r session-info}
sessionInfo()
```


## Summary

This report provides a complete summary of the system and R environment to aid in reproducibility of analyses. This document along with our code and data ensure that others can replicate our results under a similar computational setup.

